Final Project Draft #2

### 2022-04-26 draft2.Rmd
joce adding map

```{r}
healthy_data_2 %>% 
  filter(country == "Canada")

# Get the map information
world <- get_stamenmap(
    bbox = c(left = -180, bottom = -57, right = 179, top = 82.1), 
    maptype = "terrain",
    zoom = 2)

# Plot the points on the map
ggmap(world) + # creates the map "background"
  geom_point(data = healthy_data_2 %>% 
  filter(country == "Canada"), 
             aes(x = Longitude, y = Latitude), 
             size = 0.5, color = "red") +
  theme_map()
```

>>>>

```{r}
# Get the map information
world <- get_stamenmap(
    bbox = c(left = -180, bottom = -57, right = 179, top = 82.1), 
    maptype = "toner-lite",
    zoom = 2)

# Plot the points on the map
map <- ggmap(world) + # creates the map "background"
  geom_point(data = healthy_data_2, 
             aes(x = Longitude, y = Latitude), 
             size = 0.5, color = "red") +
  theme_map()

ggplotly(map,
         tooltip = c("text", "City"))
```
